### 2020-03-17 appendix.tex
stuff

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{figheatmap_03.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{figheatmap_R0_03.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{figheatmap_08.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{figheatmap_R0_08.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{figheatmap_kappa_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the generation-interval dispersion of asymptomatic cases.
(A) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
Solid lines show contours for $q$ and \Ro\ values.
Here, we assume $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
}
\end{center}
\end{figure*}

>>>>

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{figheatmap_03.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{figheatmap_R0_03.pdf}
\caption{EEffects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are narrow. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.3$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{figheatmap_08.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{figheatmap_R0_08.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases when generation-interval distributions are wide. 
Here, we assume $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.8$.
See Figure 1 in the main text for figure caption.
}
\end{center}
\end{figure*}

@@

\begin{figure*}[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{figheatmap_kappa.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.45\textwidth]{figheatmap_kappa_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the realized proportion of asymptomatic transmission and basic reproduction number, given variation in
the generation-interval dispersion of asymptomatic cases.
(A) Wide/narrow generation intervals of asymptomatic cases increase/decrease the relevance of asymptomatic cases, $q$.
(B) Wide/narrow generation intervals of asymptomatic cases decrease/increase the basic reproduction number ${\cal{R}}_0$.
Solid lines show contours for $q$ and \Ro\ values.
Here, we assume $1/r=7$ days, $\bar G_s=\bar G_a=8$ days, and $\kappa_s=0.5$.
}
\end{center}
\end{figure*}
